\section{Modern Deep Architectures}
\q{MNIST is a gray-scale dataset (32 × 32 × 1). What is the shape of
the first filter, i.e. height, width and depth?}

\q{Note as the network becomes deeper, the number of filters increases.
Why don’t we have many filters in the first convolutional layer?}

\q{LeNet: What is the main difference of the output and loss functions
compared to the current classification formulation?}

\q{What is the loss function since the network is designed for
classification?}

\q{How can we replace the 7 × 7 kernel to reduce the number of the
parameters?}

\q{Inception-Module: What is the limitation of the module?}

\q{What is a ResNet?}

\q{Bad performance for very deep networks: What could be the reason that causes the problem?}

\q{How many times has the learning rate been reduced? (Slide 35)}

\q{What is the outcome from these two figures? Which network
architecture should one pick? (Slide 39)}

\q{How can we facilitate the design of a neural network architecture?}

\q{How can we learn representations from point cloud data?}

\q{How can we build a neural network
that performs the above operation? (The input is an unordered point set; The output is a feature vector that
describes that point set; Independent from the order, the output
representation remains the same.)}

\q{What is more expensive: The PointNet with MLP networks or a
network with 3D convolutions on voxels?}

\q{What are the advantages and disadvantages of voxel-based methods?}

\q{Imagine that we aim to classify each pixel. Is this possbile with the
above architecture? (CNN with fully connceted classifier)}

\q{What are a few applications where an FCN would be necessary?}

\q{How can we make predictions on the spatial resolution of the input?}

\q{Given an image 227 × 227 × 3, we would like to predict the following
classes for each image location: water, vegetation, ground and
background. What are the dimensions of the output FCN?}

\q{Up-sampling closer to the input resolution gives more dense
predictions. Which disadvantage does this have?}

\q{Dilated convolution: What is the advantage of transforming a convolution from 1 × 3 to
1 × 5?}

\q{How can we make a deep neural network smaller and faster?}
